Open source landscape ecology tools

### 2020-07-21 paper/paper.Rmd
adds some new ideas

<!-- access to spatial data -->
<!-- rgee -->

@@

<!-- the role of data preparation - cropping, reprojecting, changing resolution/simplifying, merging/joining -->

>>>>

<!-- mention different data types/formats/projections/extents/resolutions -->
<!-- access to spatial data -->
<!-- rgee -->

@@

As we mentioned in the previous sections, obtained data can be represented by different data types and stored in various file formats and read into R using one of the packages from Section \@ref(sec:spatrep).
However, several potential obstacles to applying this data for ecological analysis still exist.

<!-- geographic/projected CRS -->
<!-- reprojecting -->
<!-- Different data can also used one of many coordinate reference systems (CRS) -->

<!-- different extents -->
<!-- cropping -->

<!-- the role of data preparation - changing resolution/simplifying, merging/joining -->
